Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-26 inst/paper/main.tex
abstract

\title{A Large-Scale Study of the Use of Eval in R}
\titlerunning{Eval in R}

@@

\bibliographystyle{plainurl}

@@

\begin{abstract}
  The \eval function turns text into code. From the point of view of
  reasoning about software system, uses of \eval turn the program's code
  from a statically known quantity that can be reasoned about and analyzed
  into one of the inputs to the program. Thus, widespread use of \eval
  hinders our ability to provide safety and security guarantees for
  software. Understanding how \eval is used in practice is key to finding
  ways to mitigate its damage. One question that has not been studied is
  whether the usage of \eval is dependent on the application domain or other
  features of the language. This paper is a large-scale study of a corpus of
  \CorpusAllCodeRnd lines of data science libraries and end-user code written in
  the R language. We performed a sophisticated dynamic analysis to confirm
  that \eval is indeed in wide spread use, and categorized patterns of
  usage. We found that \eval in this code base is more dangerous in some
  ways, and safer in others, than what was previously reported for
  JavaScript.
\end{abstract}

>>>>

\title{Why do we Eval?\\[2mm]\Large
A large-scale study of Eval usage in R}
\titlerunning{Eval in R}

@@

@@

\begin{abstract}
  \noindent Most dynamic languages allow users to turn text into code
  using various functions, often named \eval, with language-dependent
  semantics. The widespread use of these reflective functions hinders
  static analysis and prevents compilers from performing many
  optimizations. This paper aims to provide a better sense of why
  programmers use \eval.  Understanding how \eval is used in practice
  is key to finding ways to mitigate its negative impact. We have
  reasons to believe that reflective feature usage is language and
  application domain specific. In this paper, we focus on data science
  code written in R, and compare our results to previous work that
  analyzed web programming in JavaScript.  We conduct a large-scale
  study of a corpus of \CorpusAllCodeRnd lines of libraries and
  end-user code on which we performed dynamic analysis to confirm that
  \eval is indeed in widespread use, and categorized patterns of
  usage. We found that \eval is more dangerous in some ways, and safer
  in others, than what was previously reported for JavaScript.
\end{abstract}
